Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-07 WSSSPE2_report/WSSSPE2_review.tex
Section 3: make placeholder for citation.

Neil Chue Hong is currently serving as the Director of the Software
Sustainability Institute (SSI), United Kingdom. Chue Hong started with making
the point that world-leading research relies on software, quoting Kersten Kleese
Van Dam of the Pacific Northwestern National Laboratory via a petition campaign at \katznote{add cite for the petition} 
change.org, ``\emph{Today there are very few science
areas left which do not rely on IT and thus software for the majority of the
their research work. More importantly key scientific advances in experimental
and observational science would have been impossible without better software.}''
He also cited Daniel Katz, Software Infrastructure for Sustained Innovation
(SI2) Program Director of the National Science Foundation, ``\emph{Scientific
discovery and innovation are advancing along fundamentally new pathways opened
by development of increasingly sophisticated software. Software is an integral
enabler of computation, experiment and theory, and directly responsible for
increased scientific productivity and enhancement of researchers'
capabilities.}''

>>>>

Neil Chue Hong is currently serving as the Director of the Software
Sustainability Institute (SSI), United Kingdom. Chue Hong started with making
the point that world-leading research relies on software, quoting Kersten Kleese
Van Dam of the Pacific Northwestern National Laboratory via a petition campaign\footnote{\katznote{add cite for the petition}} at
change.org, ``\emph{Today there are very few science
areas left which do not rely on IT and thus software for the majority of the
their research work. More importantly key scientific advances in experimental
and observational science would have been impossible without better software.}''
He also cited Daniel Katz, Software Infrastructure for Sustained Innovation
(SI2) Program Director of the National Science Foundation, ``\emph{Scientific
discovery and innovation are advancing along fundamentally new pathways opened
by development of increasingly sophisticated software. Software is an integral
enabler of computation, experiment and theory, and directly responsible for
increased scientific productivity and enhancement of researchers'
capabilities.}''
